rotation_runs2019

### 2019-09-13 inst/documents/rotation_runs2019.Rmd
settin up rot vs seq runs

---
title: "rotation runs 2019"
output: pdf_document
#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

# read an experiment file specifying ranges
inex <- read_in_expt("in_rotations_paper_2019_inssame_freq.csv", nscenarios=1)

#inex <- read_in_expt("_in_expt_rotations_default_one_scenario.csv", nscenarios=1)

# create an object containing inputs for all scenarios
linmulti <- set_run_inputs(inex=inex)
linmulti <- set_run_inputs()

# get inputs for a single scenario
linputs <- get_one_in(linmulti, scen_num=2)

# run one scenario
dfres <- do.call(run_rot, linputs)

>>>>

---
title: "rotation_runs2019"
output: pdf_document
#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

# options
# i) run each scenario for rotation then sequence and calculate difference in the loop
# ii) run each scenario for rotation then sequence and save gens_under_thresh for each in the output file

nscenarios <- 10

# read an experiment file specifying ranges
inex <- read_in_expt("expt_rot_mort_dispersal.csv", nscenarios=nscenarios)

# create an object containing inputs for all scenarios
linmulti <- set_run_inputs(inex=inex)

# run all scenarios
for(i in 1:nscenarios)
{
  linputs <- get_one_in(linmulti, scen_num=i)

  # to compare sequence to rotation run all the scenarios above for both seq & rot 
  for(rot_or_not in 0:1)
  {  
    #to get rot_int of 0 in alternate runs - the other run uses the value from the input file
    if (rot_or_not == 0) linputs$rot_interval <- 0

    ##################
    # run one scenario
    dfres <- do.call(run_rot, linputs)

    # summarise results per scenario
    # note this is also currently calc at end of run_rot() here is probably better
    gens <- gens_under_thresh(dfres)

    # to be able to save as for rot or seq
    if ( linputs$rot_interval == 0 ) {gens_seq <- as.numeric(gens)}
    else                             {gens_rot <- as.numeric(gens)}

  } #end rot_or_not loop

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, id=i))
  df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

  # if the first scenario create df to store results of all scenarios
  if (i==1)
  {
    df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=n_scenarios))
    names(df_res_all) <- names(df_in_out)
  }

  #putting results into one row of overall results dataframe
  df_res_all[i,] <- df_in_out

} #end scenario loop

### 2019-09-13 inst/documents/rotations_notes.Rmd
settin up rot vs seq runs

# TODO

CHECK THE DIFFERENCE between linputs in run_rot() which is working compared to the input csv which mostly doesn't work.

~ something is wrong both when mort_or_freq set to mort and freq

~ when set to freq the first insecticide doesn't stop being used
  when set to mort the first insecticide is just used very briefly

~ add log-normal distribution for frequency
~ how to deal with running seq vs rotations
~ there is other stuff I still need in sensi_an_rotations1.Rmd - e.g. post-processing of outputs
~ could I have multiple experiments as columns in the same input file ?

>>>>

    #now set to log-uniform 
    minlog <- log(inex$start_freqs_min,10)
    maxlog <- log(inex$start_freqs_max,10)

    linmulti$start_freqs[i] <-  10^runif(1, min=minlog, max=maxlog)

Use hist to display the distribution of values.    
hist(linmulti$start_freqs, breaks=100)

# TODO
see rotation_runs2019.Rmd & rotations-experiments-creating-201909.xlsx

~ how to deal with running seq vs rotations
~ should rotation intervals just be set yearly i.e. 10,20,30 etc.

GET FREQUENCY RUNS sorted first (easier)
I could put the expt files all into one csv to start creating them, and divide into separate files later.

~ there is other stuff I still need in sensi_an_rotations1.Rmd - e.g. post-processing of outputs
~ could I have multiple experiments as columns in the same input file ?
